### 2018-11-15 Sections/physical_architectures_for_quantum_computing.tex
Minor edits for Zixinf

\textcolor{blue}{
% 
The addition of any non-gaussian projective measurement allows universal QC using CV cluster states. Another class of such gates is the phase gate, $\exp(it\hat x^{n})$, where $n\geq 3$ (the cubic phase gate). In order to perform universal quantum computation, one needs to implement Hamiltonians of arbitrary degree. In the heisenberg picture, any Gaussian operation is at most quadratic in the Hamiltonian, and the commutators are also at most quadratic. If one can implement the cubic phase gate, the commutators will now be of degree 3 or 4, and by induction one can construct a hamiltonian of any degree \cite{kok2010introduction}.}

\color{black}

>>>>

The addition of any non-Gaussian projective measurement allows universal quantum computation using CV cluster states. Another class of such gates is the phase gate\index{Phase gate},
\begin{align}
	\exp(it\hat x^{n}),
\end{align}
where \mbox{$n\geq 3$} (the cubic phase gate\index{Cubic phase gate}). In order to perform universal quantum computation, one needs to implement Hamiltonians of arbitrary degree. In the Heisenberg picture, any Gaussian operation is at most quadratic in the Hamiltonian, and the commutators are also at most quadratic. If one can implement the cubic phase gate, the commutators will now be of degree 3 or 4, and by induction one can construct a Hamiltonian of any degree \cite{bib:kok2010introduction}.
